The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-09 article.tex
Small tweaks

 To evaluate the performance of the CDK molecular formula generator, we
compared its runtimes to those of the classic, full enumeration-based HR2
formula generator~\cite{Kind2007} and those of a recently developed Parallel
Formula Generator (PFG)~\cite{Zhang2016} (Table~1\ref{tab:formula_generators}).
As inputs, we used two sets of $10\,000$ small ($< 500$~Da) and $20$ large ($>
1\,500$ and $< 3\,500$~Da) molecular mass values downloaded from the Global
Natural Products Social Molecular Networking database~\cite{wang2016}. The mass
tolerance was set to 0.001 or 0.01 Da. The CDK \cdkversion{}'s Round-Robin 
formula generator outperformed the other methods in all cases, despite running
in a single thread (PFG utilizes multiple threads). The performance gain of
the Round Robin algorithm was particularly apparent when narrow mass ranges 
were queried (e.g., $\pm 0.001$ Da), thus showing its suitability for
applications in high-resolution mass spectrometry.

@@

The SMILES generation API has also been simplified and made more flexible.
Creating unique SMILES or aromatic SMILES is now done by first creating a
SMILES generator instance which can make generic or unique SMILES, and with
or without simplifying aromatic rings using the lower case element symbols
for the organic subset. This generator can then be repeatedly called:

>>>>

 To evaluate the performance of the CDK molecular formula generator, we
compared its runtimes to those of the classic, full enumeration-based HR2
formula generator~\cite{Kind2007} and those of a recently developed Parallel
Formula Generator (PFG)~\cite{Zhang2016} (Table~1\ref{tab:formula_generators}).
As inputs, we used two sets of $10\,000$ small ($< 500$~Da) and $20$ large ($>
1\,500$ and $< 3\,500$~Da) molecular mass values downloaded from the Global
Natural Products Social Molecular Networking database~\cite{wang2016}. The mass
tolerance was set to 0.001 or 0.01 Da. The CDK \cdkversion{}'s Round-Robin 
formula generator outperformed the other methods in all cases, despite running
in a single thread (PFG utilizes multiple threads). The performance gain of
the Round Robin algorithm was particularly apparent when narrow mass ranges 
were queried (e.g. $\pm 0.001$ Da), thus showing its suitability for
applications in high-resolution mass spectrometry.

@@

The SMILES generation API has also been simplified and made more flexible.
Creating unique SMILES or aromatic SMILES is now done by first creating a
SMILES generator instance which can make generic or unique SMILES, and with
or without simplifying aromatic rings using the lower case element symbols
for the organic subset. This generator can then be called repeatedly:
